---
title: "Aviation Marketing"
author: "Omar Ossama"
output: html_document
---

## Setting the working directory
```{r}
setwd ("C:/Users/omaro/Documents/DSBA/06-Capstone Project")
```

## Libraries to be used
```{r}
library(esquisse)      #Plotting tool
library(ggplot2)       #Plotting tool
library(gridExtra)     #Plotting tool
library(corrplot)      #Plot corelation between numerical varaibles
library(mice)          #Missing data treatment
library(caTools)       #Splitting the dataset
library(caret)         #Building confusion matrix and comparing models
library(rpart.plot)    #Tunning CART model
library(rpart)         #Evaluating CART model
library(rattle)        #Visulaizing CART model
library(randomForest)  #Tunning RF model
```

## Importing the data
```{r}
aviation1 = read.csv("Aviation_Marketing Project-Survey data.csv", header = T, na.strings = c(""," "))
aviation2 = read.csv("Aviation_Marketing Project-Flight data.csv", header = T, na.strings = c(""," "))
```

## Editing column name and performing data join
```{r}
names(aviation1) [names(aviation1) == 'CustomerId'] <- 'CustomerID'

aviation = merge(x = aviation1, y = aviation2, by = "CustomerID", all = TRUE)
```

## Data summary
```{r}
dim(aviation)
summary(aviation)
str(aviation)
sum(is.na(aviation))
```

## Editting variable types
```{r}
colnames(aviation) = make.names(colnames(aviation))

aviation$Satisfaction = as.factor(aviation$Satisfaction)
aviation$Seat_comfort = as.factor(aviation$Seat_comfort)
aviation$Departure.Arrival.time_convenient = as.factor(aviation$Departure.Arrival.time_convenient)
aviation$Food_drink = as.factor(aviation$Food_drink)
aviation$Gate_location = as.factor(aviation$Gate_location)
aviation$Inflightwifi_service = as.factor(aviation$Inflightwifi_service)
aviation$Inflight_entertainment = as.factor(aviation$Inflight_entertainment)
aviation$Online_support = as.factor(aviation$Online_support)
aviation$Ease_of_Onlinebooking = as.factor(aviation$Ease_of_Onlinebooking)
aviation$Onboard_service = as.factor(aviation$Onboard_service)
aviation$Leg_room_service = as.factor(aviation$Leg_room_service)
aviation$Baggage_handling = as.factor(aviation$Baggage_handling)
aviation$Checkin_service = as.factor(aviation$Checkin_service)
aviation$Cleanliness = as.factor(aviation$Cleanliness)
aviation$Online_boarding = as.factor(aviation$Online_boarding)
aviation$Gender = as.factor(aviation$Gender)
aviation$CustomerType = as.factor(aviation$CustomerType)
aviation$TypeTravel = as.factor(aviation$TypeTravel)
aviation$Class = as.factor(aviation$Class)
aviation$Flight_Distance = as.numeric(aviation$Flight_Distance)
aviation$DepartureDelayin_Mins = as.numeric(aviation$DepartureDelayin_Mins)
aviation$ArrivalDelayin_Mins = as.numeric(aviation$ArrivalDelayin_Mins)

```


## Univarite analysis
```{r}

prop.table(table(aviation$Satisfaction))

ggplot(aviation) +
  aes(x = Satisfaction) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Seat_comfort))

ggplot(aviation) +
  aes(x = Seat_comfort) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Departure.Arrival.time_convenient))

ggplot(aviation) +
  aes(x = Departure.Arrival.time_convenient) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Food_drink))

ggplot(aviation) +
  aes(x = Food_drink) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Gate_location))

ggplot(aviation) +
  aes(x = Gate_location) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Inflightwifi_service))

ggplot(aviation) +
  aes(x = Inflightwifi_service) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Inflight_entertainment))

ggplot(aviation) +
  aes(x = Inflight_entertainment) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Online_support))

ggplot(aviation) +
  aes(x = Online_support) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Ease_of_Onlinebooking))

ggplot(aviation) +
  aes(x = Ease_of_Onlinebooking) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Onboard_service))

ggplot(aviation) +
  aes(x = Onboard_service) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Leg_room_service))

ggplot(aviation) +
  aes(x = Leg_room_service) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Baggage_handling))

ggplot(aviation) +
  aes(x = Baggage_handling) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Checkin_service))

ggplot(aviation) +
  aes(x = Checkin_service) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Cleanliness))

ggplot(aviation) +
  aes(x = Cleanliness) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Online_boarding))

ggplot(aviation) +
  aes(x = Online_boarding) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Gender))

ggplot(aviation) +
  aes(x = Gender) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$CustomerType))

ggplot(aviation) +
  aes(x = CustomerType) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$TypeTravel))

ggplot(aviation) +
  aes(x = TypeTravel) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


prop.table(table(aviation$Class))

ggplot(aviation) +
  aes(x = Class) +
  geom_bar(fill = "#0c4c8a") +
  theme_minimal()


```

## Creating function to combine histograms and boxplots
```{r}
plot_histogram_n_boxplot = function(variable, variableNameString, binw){
  h = ggplot(data = aviation, aes(x= variable))+
    labs(x = variableNameString,y ='Count')+
    geom_histogram(fill = 'green',col = 'red',binwidth = binw)+
    geom_vline(aes(xintercept=mean(variable)),
               color="black", linetype="dashed", size=0.5)
  b = ggplot(data = aviation, aes('',variable))+ 
    geom_boxplot(outlier.colour = 'red',col = 'red',outlier.shape = 19)+
    labs(x = '',y = variableNameString)+ coord_flip()
  grid.arrange(h,b,ncol = 2)
}
```

## Creating histograms and boxplots for the numerical variables
```{r}
plot_histogram_n_boxplot(aviation$Age, 'Age', 1)

plot_histogram_n_boxplot(aviation$Flight_Distance, 'Flight Distance', 1)

plot_histogram_n_boxplot(aviation$DepartureDelayin_Mins, 'Departure Delay in Mins', 1)

plot_histogram_n_boxplot(aviation$ArrivalDelayin_Mins, 'Arrival Delay in Mins', 1)
```

## Bivariate analysis for the dependent variable
```{r}

chisq.test(aviation$Satisfaction, aviation$Seat_comfort)
ggplot(aviation, aes(fill = Satisfaction, x = Seat_comfort)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Departure.Arrival.time_convenient)
ggplot(aviation, aes(fill = Satisfaction, x = Departure.Arrival.time_convenient)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Food_drink)
ggplot(aviation, aes(fill = Satisfaction, x = Food_drink)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Gate_location)
ggplot(aviation, aes(fill = Satisfaction, x = Gate_location)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Inflightwifi_service)
ggplot(aviation, aes(fill = Satisfaction, x = Inflightwifi_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Inflight_entertainment)
ggplot(aviation, aes(fill = Satisfaction, x = Inflight_entertainment)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Online_support)
ggplot(aviation, aes(fill = Satisfaction, x = Online_support)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Ease_of_Onlinebooking)
ggplot(aviation, aes(fill = Satisfaction, x = Ease_of_Onlinebooking)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Onboard_service)
ggplot(aviation, aes(fill = Satisfaction, x = Onboard_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Leg_room_service)
ggplot(aviation, aes(fill = Satisfaction, x = Leg_room_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Baggage_handling)
ggplot(aviation, aes(fill = Satisfaction, x = Baggage_handling)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Checkin_service)
ggplot(aviation, aes(fill = Satisfaction, x = Checkin_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Cleanliness)
ggplot(aviation, aes(fill = Satisfaction, x = Cleanliness)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Online_boarding)
ggplot(aviation, aes(fill = Satisfaction, x = Online_boarding)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Gender)
ggplot(aviation, aes(fill = Satisfaction, x = Gender)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$CustomerType)
ggplot(aviation, aes(fill = Satisfaction, x = CustomerType)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$TypeTravel)
ggplot(aviation, aes(fill = Satisfaction, x = TypeTravel)) + 
  geom_bar(position="fill")

chisq.test(aviation$Satisfaction, aviation$Class)
ggplot(aviation, aes(fill = Satisfaction, x = Class)) + 
  geom_bar(position="fill")



ggplot(aviation, aes(fill = Satisfaction, x = cut(Age, 5))) + 
  geom_bar(position="fill") + labs(x = 'Age',y ='Count')

ggplot(aviation, aes(fill = Satisfaction, x = cut(Flight_Distance, 5))) + 
  geom_bar(position="fill") + labs(x = 'Flight Distance',y ='Count')

ggplot(aviation, aes(fill = Satisfaction, x = cut(DepartureDelayin_Mins, 5))) + 
  geom_bar(position="fill") + labs(x = 'Deparute Delay in Mins',y ='Count')

ggplot(aviation, aes(fill = Satisfaction, x = cut(ArrivalDelayin_Mins, 5))) + 
  geom_bar(position="fill") + labs(x = 'Arrival Delay in Mins',y ='Count')

```

## Multivariate analysis for the numerical variables
```{r}
corrplot(cor(aviation[c(19,22:24)]),type="lower",method="number")
```

## Bivariate analysis for random variables
```{r}

chisq.test(aviation$Seat_comfort, aviation$Leg_room_service)
ggplot(aviation, aes(fill = Seat_comfort, x = Leg_room_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Food_drink, aviation$Onboard_service)
ggplot(aviation, aes(fill = Food_drink, x = Onboard_service)) + 
  geom_bar(position="fill")

chisq.test(aviation$Ease_of_Onlinebooking, aviation$Online_support)
ggplot(aviation, aes(fill = Ease_of_Onlinebooking, x = Online_support)) + 
  geom_bar(position="fill")

chisq.test(aviation$Checkin_service, aviation$Baggage_handling)
ggplot(aviation, aes(fill = Checkin_service, x = Baggage_handling)) + 
  geom_bar(position="fill")

```

##Removing Customer ID variable
```{r}
aviation$CustomerID <- NULL
```

## Missing data treatment
```{r}
init.impute = mice(aviation, m=2, method = "pmm", seed = 1000)
aviation = complete(init.impute, 2)
sum(is.na(aviation))
```

##Outlier treatment
```{r}

quantile(aviation$Flight_Distance, probs = seq(0,1,0.05))
aviation$Flight_Distance[which(aviation$Flight_Distance > 3833)] <- 3833

quantile(aviation$DepartureDelayin_Mins, probs = seq(0,1,0.05))
aviation$DepartureDelayin_Mins[which(aviation$DepartureDelayin_Mins > 76)] <- 76

quantile(aviation$ArrivalDelayin_Mins, probs = seq(0,1,0.05))
aviation$ArrivalDelayin_Mins[which(aviation$ArrivalDelayin_Mins > 78)] <- 78

```

##Creating Inflight COmfort variable
```{r}
#Editing Seat Comfort
aviation$Seat_comfort <- as.character(aviation$Seat_comfort)

aviation$Seat_comfort[aviation$Seat_comfort=="excellent"] <- "5"
aviation$Seat_comfort[aviation$Seat_comfort=="good"] <- "4"
aviation$Seat_comfort[aviation$Seat_comfort=="acceptable"] <- "3"
aviation$Seat_comfort[aviation$Seat_comfort=="need improvement"] <- "2"
aviation$Seat_comfort[aviation$Seat_comfort=="poor"] <- "1"
aviation$Seat_comfort[aviation$Seat_comfort=="extremely poor"] <- "0"

aviation$Seat_comfort <- as.numeric(aviation$Seat_comfort)

#Editing Leg room
aviation$Leg_room_service <- as.character(aviation$Leg_room_service)

aviation$Leg_room_service[aviation$Leg_room_service=="excellent"] <- "5"
aviation$Leg_room_service[aviation$Leg_room_service=="good"] <- "4"
aviation$Leg_room_service[aviation$Leg_room_service=="acceptable"] <- "3"
aviation$Leg_room_service[aviation$Leg_room_service=="need improvement"] <- "2"
aviation$Leg_room_service[aviation$Leg_room_service=="poor"] <- "1"
aviation$Leg_room_service[aviation$Leg_room_service=="extremely poor"] <- "0"

aviation$Leg_room_service <- as.numeric(aviation$Leg_room_service)

#Creating new variable
aviation$Inflight_comfort = ((aviation$Seat_comfort)+(aviation$Leg_room_service))/2
```

##Creating Inflight Services variable
```{r}
#Editing Food & drink
aviation$Food_drink <- as.character(aviation$Food_drink)

aviation$Food_drink[aviation$Food_drink=="excellent"] <- "5"
aviation$Food_drink[aviation$Food_drink=="good"] <- "4"
aviation$Food_drink[aviation$Food_drink=="acceptable"] <- "3"
aviation$Food_drink[aviation$Food_drink=="need improvement"] <- "2"
aviation$Food_drink[aviation$Food_drink=="poor"] <- "1"
aviation$Food_drink[aviation$Food_drink=="extremely poor"] <- "0"

aviation$Food_drink <- as.numeric(aviation$Food_drink)

#Editing Inflight WiFi
aviation$Inflightwifi_service <- as.character(aviation$Inflightwifi_service)

aviation$Inflightwifi_service[aviation$Inflightwifi_service=="excellent"] <- "5"
aviation$Inflightwifi_service[aviation$Inflightwifi_service=="good"] <- "4"
aviation$Inflightwifi_service[aviation$Inflightwifi_service=="acceptable"] <- "3"
aviation$Inflightwifi_service[aviation$Inflightwifi_service=="need improvement"] <- "2"
aviation$Inflightwifi_service[aviation$Inflightwifi_service=="poor"] <- "1"
aviation$Inflightwifi_service[aviation$Inflightwifi_service=="extremely poor"] <- "0"

aviation$Inflightwifi_service <- as.numeric(aviation$Inflightwifi_service)

#Editing Inflight Entertainment
aviation$Inflight_entertainment <- as.character(aviation$Inflight_entertainment)

aviation$Inflight_entertainment[aviation$Inflight_entertainment=="excellent"] <- "5"
aviation$Inflight_entertainment[aviation$Inflight_entertainment=="good"] <- "4"
aviation$Inflight_entertainment[aviation$Inflight_entertainment=="acceptable"] <- "3"
aviation$Inflight_entertainment[aviation$Inflight_entertainment=="need improvement"] <- "2"
aviation$Inflight_entertainment[aviation$Inflight_entertainment=="poor"] <- "1"
aviation$Inflight_entertainment[aviation$Inflight_entertainment=="extremely poor"] <- "0"

aviation$Inflight_entertainment <- as.numeric(aviation$Inflight_entertainment)

#Editing Onboard Service
aviation$Onboard_service <- as.character(aviation$Onboard_service)

aviation$Onboard_service[aviation$Onboard_service=="excellent"] <- "5"
aviation$Onboard_service[aviation$Onboard_service=="good"] <- "4"
aviation$Onboard_service[aviation$Onboard_service=="acceptable"] <- "3"
aviation$Onboard_service[aviation$Onboard_service=="need improvement"] <- "2"
aviation$Onboard_service[aviation$Onboard_service=="poor"] <- "1"
aviation$Onboard_service[aviation$Onboard_service=="extremely poor"] <- "0"

aviation$Onboard_service <- as.numeric(aviation$Onboard_service)

#Editing Cleanliness
aviation$Cleanliness <- as.character(aviation$Cleanliness)

aviation$Cleanliness[aviation$Cleanliness=="excellent"] <- "5"
aviation$Cleanliness[aviation$Cleanliness=="good"] <- "4"
aviation$Cleanliness[aviation$Cleanliness=="acceptable"] <- "3"
aviation$Cleanliness[aviation$Cleanliness=="need improvement"] <- "2"
aviation$Cleanliness[aviation$Cleanliness=="poor"] <- "1"
aviation$Cleanliness[aviation$Cleanliness=="extremely poor"] <- "0"

aviation$Cleanliness <- as.numeric(aviation$Cleanliness)

#Creating new variable
aviation$Inflight_services = ((aviation$Food_drink)
                                    +(aviation$Inflightwifi_service)
                                    +(aviation$Inflight_entertainment)
                                    +(aviation$Onboard_service)
                                    +(aviation$Cleanliness))/5


```

##Creating online services variable
```{r}
#Editing online support
aviation$Online_support <- as.character(aviation$Online_support)

aviation$Online_support[aviation$Online_support=="excellent"] <- "5"
aviation$Online_support[aviation$Online_support=="good"] <- "4"
aviation$Online_support[aviation$Online_support=="acceptable"] <- "3"
aviation$Online_support[aviation$Online_support=="need improvement"] <- "2"
aviation$Online_support[aviation$Online_support=="poor"] <- "1"
aviation$Online_support[aviation$Online_support=="extremely poor"] <- "0"

aviation$Online_support <- as.numeric(aviation$Online_support)

#Editing Ease of online booking
aviation$Ease_of_Onlinebooking <- as.character(aviation$Ease_of_Onlinebooking)

aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="excellent"] <- "5"
aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="good"] <- "4"
aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="acceptable"] <- "3"
aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="need improvement"] <- "2"
aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="poor"] <- "1"
aviation$Ease_of_Onlinebooking[aviation$Ease_of_Onlinebooking=="extremely poor"] <- "0"

aviation$Ease_of_Onlinebooking <- as.numeric(aviation$Ease_of_Onlinebooking)

#Editing online boarding
aviation$Online_boarding <- as.character(aviation$Online_boarding)

aviation$Online_boarding[aviation$Online_boarding=="excellent"] <- "5"
aviation$Online_boarding[aviation$Online_boarding=="good"] <- "4"
aviation$Online_boarding[aviation$Online_boarding=="acceptable"] <- "3"
aviation$Online_boarding[aviation$Online_boarding=="need improvement"] <- "2"
aviation$Online_boarding[aviation$Online_boarding=="poor"] <- "1"
aviation$Online_boarding[aviation$Online_boarding=="extremely poor"] <- "0"

aviation$Online_boarding <- as.numeric(aviation$Online_boarding)

#Creating new variable
aviation$Online_service = ((aviation$Online_support)
                           +(aviation$Online_boarding)
                           +(aviation$Ease_of_Onlinebooking))/3
```

##Creating Pre/post flight services variable
```{r}
#Editing Departure and arrival time convinience
aviation$Departure.Arrival.time_convenient <- as.character(aviation$Departure.Arrival.time_convenient)

aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="excellent"] <- "5"
aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="good"] <- "4"
aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="acceptable"] <- "3"
aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="need improvement"] <- "2"
aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="poor"] <- "1"
aviation$Departure.Arrival.time_convenient[aviation$Departure.Arrival.time_convenient=="extremely poor"] <- "0"

aviation$Departure.Arrival.time_convenient <- as.numeric(aviation$Departure.Arrival.time_convenient)

#Editing Gate location
aviation$Gate_location <- as.character(aviation$Gate_location)

aviation$Gate_location[aviation$Gate_location=="very convinient"] <- "5"
aviation$Gate_location[aviation$Gate_location=="Convinient"] <- "4"
aviation$Gate_location[aviation$Gate_location=="manageable"] <- "3"
aviation$Gate_location[aviation$Gate_location=="need improvement"] <- "2"
aviation$Gate_location[aviation$Gate_location=="Inconvinient"] <- "1"
aviation$Gate_location[aviation$Gate_location=="very inconvinient"] <- "0"

aviation$Gate_location <- as.numeric(aviation$Gate_location)

#Editing Baggage handling
aviation$Baggage_handling <- as.character(aviation$Baggage_handling)

aviation$Baggage_handling[aviation$Baggage_handling=="excellent"] <- "5"
aviation$Baggage_handling[aviation$Baggage_handling=="good"] <- "4"
aviation$Baggage_handling[aviation$Baggage_handling=="acceptable"] <- "3"
aviation$Baggage_handling[aviation$Baggage_handling=="need improvement"] <- "2"
aviation$Baggage_handling[aviation$Baggage_handling=="poor"] <- "1"
aviation$Baggage_handling[aviation$Baggage_handling=="extremely poor"] <- "0"

aviation$Baggage_handling <- as.numeric(aviation$Baggage_handling)

#Editing Check-in service
aviation$Checkin_service <- as.character(aviation$Checkin_service)

aviation$Checkin_service[aviation$Checkin_service=="excellent"] <- "5"
aviation$Checkin_service[aviation$Checkin_service=="good"] <- "4"
aviation$Checkin_service[aviation$Checkin_service=="acceptable"] <- "3"
aviation$Checkin_service[aviation$Checkin_service=="need improvement"] <- "2"
aviation$Checkin_service[aviation$Checkin_service=="poor"] <- "1"
aviation$Checkin_service[aviation$Checkin_service=="extremely poor"] <- "0"

aviation$Checkin_service <- as.numeric(aviation$Checkin_service)

#Creating new variable
aviation$pre.post.flight = ((aviation$Departure.Arrival.time_convenient)
                           +(aviation$Gate_location)
                           +(aviation$Baggage_handling)
                           +(aviation$Checkin_service))/4

```

##Editiing the dependent variable levels
```{r}
aviation$Satisfaction <- as.character(aviation$Satisfaction)

aviation$Satisfaction[aviation$Satisfaction=="neutral or dissatisfied"] <- "No"
aviation$Satisfaction[aviation$Satisfaction=="satisfied"] <- "Yes"

aviation$Satisfaction <- as.factor(aviation$Satisfaction)
```

##Checking for multicollinerity
```{r}

corrplot(cor(aviation[c(3,5:10)]),type="lower",method="number")

chisq.test(aviation$Gender, aviation$CustomerType)

chisq.test(aviation$Gender, aviation$TypeTravel)

chisq.test(aviation$Gender, aviation$Class)

chisq.test(aviation$CustomerType, aviation$TypeTravel)

chisq.test(aviation$CustomerType, aviation$Class)

chisq.test(aviation$TypeTravel, aviation$Class)

```

##Splitting data into train and test sets
```{r}
set.seed(1000)

sample = sample.split(aviation$Satisfaction,SplitRatio = 0.7)
train = subset(aviation,sample == TRUE)
test = subset(aviation,sample == FALSE)

dim(train)
dim(test)

prop.table(table(train$Satisfaction))
prop.table(table(test$Satisfaction))
```

##CART model
```{r}
r.ctrl = rpart.control(minsplit = 10, minbucket = 3, xval = 10)

cart_model <- rpart(formula = Satisfaction~., data = train, method = "class", control = r.ctrl)
cart_model
fancyRpartPlot(cart_model)
prp(cart_model)
```

##Pruning
```{r}
cart_model$cptable
```
No pruning required

##Variable importance
```{r}
cart_model$variable.importance
```

##CART model performance
```{r}
cart_train_pred <- predict(cart_model, train, type="class")

caret::confusionMatrix(cart_train_pred, train$Satisfaction)

cart_test_pred <- predict(cart_model, test, type = "class")

caret::confusionMatrix(cart_test_pred, test$Satisfaction)
```
Train:  Accuracy = 86.76%
        Sensitivity = 86.39%
        Specificity = 87.06%
        
Test:   Accuracy = 87.04%
        Sensitivity = 86.94%
        Specificity = 87.12%
        
##Training model parameters
```{r}
fitControl <- trainControl(
              method = 'repeatedcv',
              number = 4,
              repeats = 1,
              allowParallel = TRUE,
              classProbs = TRUE,
              summaryFunction=twoClassSummary
              ) 
```

##Building logistic regression model
```{r}
lr_model <- train(Satisfaction ~.
                  -Inflight_comfort -Inflight_services -Online_service -pre.post.flight,
                  data = train,
                  method = "glm",
                  family = "binomial",
                  trControl = fitControl)

lr_model
summary(lr_model)
```
ROC = 0.9094

##Logistic regression model performance
```{r}
lr_train_pred <- predict(lr_model, newdata = train, type = "raw")

caret::confusionMatrix(lr_train_pred, train$Satisfaction)

lr_test_pred <- predict(lr_model, newdata = test, type = "raw")

caret::confusionMatrix(lr_test_pred, test$Satisfaction)
```
Train:  Accuracy = 83.59%
        Sensitivity = 81.67%
        Specificity = 85.19%
        
Test:   Accuracy = 83.43%
        Sensitivity = 81.65%
        Specificity = 84.90%
        
##Building random forest model
```{r}
rf_model <- train(Satisfaction ~ ., data = train,
                     method = "rf",
                     ntree = 30,
                     maxdepth = 5,
                     tuneLength = 10,
                     trControl = fitControl)

rf_model
```
ROC = 0.9898

##Random forest model performance
```{r}
rf_train_pred <- predict(rf_model, newdata = train, type = "raw")

caret::confusionMatrix(rf_train_pred, train$Satisfaction)

rf_test_pred <- predict(rf_model, newdata = test, type = "raw")

caret::confusionMatrix(rf_test_pred, test$Satisfaction)
```
Train:  Accuracy = 99.97%
        Sensitivity = 99.98%
        Specificity = 99.96%
        
Test:   Accuracy = 94.85%
        Sensitivity = 95.48%
        Specificity = 94.33%

##Variable importance
```{r}
varImp(rf_model, scale=FALSE)
```

##Extreme Gradient Boosting model
```{r}
cv_ctrl <- trainControl(method = "repeatedcv", repeats = 1,number = 3, 
                        summaryFunction = twoClassSummary,
                        classProbs = TRUE,
                        allowParallel=T)

    xgb_grid <- expand.grid(nrounds = 100,
                            eta = c(0.01),
                            max_depth = 4,
                            gamma = 0,
                            colsample_bytree = 1,    
                            min_child_weight = 1,    
                            subsample = 1            
    )

    xgb_model <-train(Satisfaction~.,
                     data=train,
                     method="xgbTree",
                     trControl=cv_ctrl,
                     tuneGrid=xgb_grid,
                     verbose=T,
                     nthread = 2
    )
    
xgb_model
```
ROC = 0.9529

##XGB model performance
```{r}
xgb_train_pred <- predict(xgb_model, newdata = train, type = "raw")

caret::confusionMatrix(xgb_train_pred, train$Satisfaction)

xgb_test_pred <- predict(xgb_model, newdata = test, type = "raw")

caret::confusionMatrix(xgb_test_pred, test$Satisfaction)
```
Train:  Accuracy = 87.97%
        Sensitivity = 87.21%
        Specificity = 88.60%
        
Test:   Accuracy = 88.07%
        Sensitivity = 87.77%
        Specificity = 88.31%
        
##Variable importance
```{r}
varImp(xgb_model, scale=FALSE)
```